Standalone Tactics using OpenTheory

### 2011-10-14 paper.tex
write paper outline and clean up tex file

\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{url}
\usepackage{xspace}
\usepackage{color}
\definecolor{linkcolor}{rgb}{0,0,0.5}
\usepackage[
  colorlinks=true,
  linkcolor=linkcolor,
  citecolor=linkcolor,
  filecolor=linkcolor,
  urlcolor=linkcolor]{hyperref}

\makeatletter
\providecommand*{\toclevel@title}{0}
\providecommand*{\toclevel@author}{1}
\makeatother

\hypersetup{bookmarksdepth=subsection}

\newcommand{\HOL}{HOL4\xspace}
\newcommand{\Squolem}{Squolem\xspace}
\newcommand{\QBV}{QBV\xspace}
\newcommand{\Minisat}{MiniSat\xspace}
\newcommand{\OpenTheory}{OpenTheory\xspace}

\newcommand{\secref}[1]{Section~\ref{#1}}
\newcommand{\figref}[1]{Figure~\ref{#1}}
\newcommand{\thmref}[1]{Theorem~\ref{#1}}
\newcommand{\eqnref}[1]{(\ref{#1})}

\newcommand{\sem}[1]{[\![{#1}]\!]}

\newcommand{\ie}{i.e., }
\newcommand{\eg}{e.g., }
\newcommand{\cf}{cf.\xspace}
\newcommand{\wrt}{wrt.\xspace}

\newcommand{\ite}[3]{\ensuremath{\mathsf{if}\ #1\ \mathsf{then}\ #2\ \mathsf{else}\ #3}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\hypersetup{
  pdfauthor = {Ramana Kumar and Joe Hurd},
  pdftitle = {Standalone Tactics using OpenTheory},
  pdfkeywords = {Interactive Theorem Proving, LCF-style proof checking, HOL, \OpenTheory},
  pdfsubject = {}
}

@@

\author{Ramana Kumar\thanks{supported by the Gates Cambridge Trust}\and Joe Hurd}

\institute{\email{rk436@cam.ac.uk} and \email{joe@galois.com}}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Introduction}
\label{sec:introduction}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Related Work}
\label{sec:related-work}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Background and Theory}
\label{sec:background}

\subsection{Quantified Boolean Formulae}

\subsection{Skolem Functions and Models}
\label{sec:models}

\subsection{Certificates of Validity}
\label{sec:certificates}

\subsection{Higher-Order Logic}
\label{sec:hol}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Implementation}
\label{sec:checking}

\subsection{Overview}
\label{sec:checking-overview}

\subsection{Subsection}
\label{sec:preproc}

\subsection{Subsection}
\label{sec:hypelim}

\subsection{Example}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experimental Results}
\label{sec:experimental-results}

\subsection{Run-Times}
\label{sec:run-times}

\subsection{Profiling and Future Improvements}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Conclusions}
\label{sec:conclusion}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\bigskip

\noindent \textbf{Acknowledgments} The authors would like to thank ....

\vspace{-\bigskipamount}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

\usepackage{url}
\usepackage{xspace}

\newcommand{\OpenTheory}{OpenTheory\xspace}

@@

@@

\author{Ramana Kumar\thanks{supported by the Gates Cambridge Trust}\inst{1}\and Joe Hurd\inst{2}}

\institute{\email{Ramana.Kumar@cl.cam.ac.uk}\and\email{joe@galois.com}}

@@

\section{Introduction}

\section{Tactics in Proof Assistants}

Examples of proof assistants.
Examples of tactics.
Examples of duplication.

\section{\OpenTheory for Tactic Communication}

Introduction to article format.
Representing terms and proofs in the format.
Viewing tactics as derived inference rules.

\section{Making Existing Tactics into Web Services}

Implementation details to make standalone.
Implementation details to put on the web.
Examples of tactics for which it is done: HolQbf, HolSmt, HolSat, sledgehammer, TFL, function package, Metis, datatype packages, arithmetic decision procedure.

\section{Performance}

Speed comparisons against using built-in tactics.
Amount of code and time required, compared to porting tactics at the implementation level.

\section{Related Work}

Evidential tool bus.
System on TPTP.
Natural extension of the integration of automatic tools into interactive systems.

\section{Conclusions}

Additional (non-proof) work tactics might also do needs to be represented on another channel.

@@
